### 2019-03-05 README.Rmd
roll back to R 3.5.0

- Install R (analysis run with `3.5.2`) and Rstudio (alternatively use Docker as outlined below).

@@

- Install the analysis dependencies and build the package using the following. To enable more robust reproducibility consider using the [`checkpoint`](https://cran.r-project.org/web/packages/checkpoint/index.html) package versioned locked to R `3.5.2`.

>>>>

- Install R (analysis run with `3.5.0`) and Rstudio (alternatively use Docker as outlined below).

@@

- Install the analysis dependencies and build the package using the following. To enable more robust reproducibility consider using the [`checkpoint`](https://cran.r-project.org/web/packages/checkpoint/index.html) package versioned locked to R `3.5.0`.
